Tutorial: Quantifying Spatially Resolved Hydration Thermodynamics Using Grid Inhomogeneous Solvation Theory [Article v\versionnumber]

### 2025-05-16 manuscript/manuscript.tex
More Clarifications
1) Clarified the use of gridcntr in section 3
2) Clarified common error of Eww being wrong

\begin{lstlisting}[style=cpptraj]
gist gridcntr <x> <y> <z> griddim <Nx> <Ny> <Nz> gridspacn <val>
\end{lstlisting}
Additionally, the GIST calculation should usually be preceded by centering the solute molecule in the unit cell and reimaging to account for periodic boundary conditions.
Often, the region of interest will be defined as the surrounding of a molecule, for example a ligand in the binding pocket or a whole protein. 
We recommend using GIST grids with a similar size to the simulation box, as the GIST calculation will usually not be the time limiting step and a region of interest can then be chosen freely in post-analysis.
However, if computation resources and disk space are limited, it might be beneficial to reduce the grid size.
The minimum recommended grid size depends on the solvent and its interactions with the solute.
Generally, a grid encompassing 2 to 3 solvent layers around the solute is sufficient. 
For TIP3P water, this corresponds to a buffer zone of around \SI{10}{\angstrom} around the solute. 
Larger grids might be necessary, for example for strongly charged solutes.

@@

While $E_{ww}$ converges nicely here when using the tabulated $E_{ww, norm}$, if it diverges you might need to tweak the $E_{ww}$ reference by either using the automatic referencing, using a different tabulated $E_{ww, norm}$ value or running a pure bulk solvent reference calculation.
\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{figures/biotin-contributions_ref.png}
	\caption{Convergence of $\dgsolv$ and its contributions with increasing distance to the solute molecule. The entropy was referenced, so it converges to zero for voxels far away from the solute.}\label{fig_radial_convergence_ref}
\end{figure}

>>>>

\begin{lstlisting}[style=cpptraj]
gist gridcntr <x> <y> <z> griddim <Nx> <Ny> <Nz> gridspacn <val>
\end{lstlisting}
If the solute is already centered at the origin (0, 0, 0), the grid center does not need to be specified.
As such, the GIST calculation should usually be preceded by centering the solute molecule in the unit cell and reimaging to account for periodic boundary conditions.
Often, the region of interest will be defined as the surrounding of a molecule, for example a ligand in the binding pocket or a whole protein. 
We recommend using GIST grids with a similar size to the simulation box, as the GIST calculation will usually not be the time limiting step and a region of interest can then be chosen freely in post-analysis.
However, if computation resources and disk space are limited, it might be beneficial to reduce the grid size.
The minimum recommended grid size depends on the solvent and its interactions with the solute.
Generally, a grid encompassing 2 to 3 solvent layers around the solute is sufficient. 
For TIP3P water, this corresponds to a buffer zone of around \SI{10}{\angstrom} around the solute. 
Larger grids might be necessary, for example for strongly charged solutes.

@@

While $E_{ww}$ converges nicely here when using the tabulated $E_{ww, norm}$, if it diverges one might need to tweak the $E_{ww}$ reference by either using the automatic referencing, using a different tabulated $E_{ww, norm}$ value or running a pure bulk solvent reference calculation.
The most common error for strong divergence of $E_{ww}$ is that the reference value is set to a value of a different solvent model.

\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{figures/biotin-contributions_ref.png}
	\caption{Convergence of $\dgsolv$ and its contributions with increasing distance to the solute molecule. The entropy was referenced, so it converges to zero for voxels far away from the solute.}\label{fig_radial_convergence_ref}
\end{figure}
